Abstract Binding Trees

### 2015-11-07 paper.tex
[paper] fix typo

%%TODO
We also have the induced maps $\Of{\nu_\Gamma}{V^{[\Gamma]}\to P^{[\Gamma]}}$
and
$\Of{\varsigma_{\Upsilon\parallel\Gamma}}{P_\tau^{\Yoneda{\Upsilon\parallel\Gamma}}
\times S^{\{\Upsilon\}}\times P^{[\Gamma]}\to P_\tau}$.

@@

Next we have the interpretation of metavariable applications
\[%
  \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
    \MApp{\MV{m}}{\vec{u}}{\vec{M}} : \tau}_P%
  \qquad(\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}})
\]
which proceeds by projecting the metavariable's interpretation from the
environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {S^{\{\Upsilon\}}} \arrow[r, "\Tuple{\pi_u}_{u\in\vec{u}}"]
    \& {S^{\{\vec{\sigma}\}}}
  \end{tikzcd}
  }\\
  \ADefine{\psi}{
   \begin{tikzcd}[ampersand replacement = \&, sep=28ex]
     {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}
        \arrow[r, "\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:q}_P}_{(M,q)\in \vec{M}\otimes\vec{\tau}}"]
     \& {P^{[\vec{\tau}]}}
   \end{tikzcd}
  }
\end{align*}

>>>>

%%TODO
We also have the induced maps $\Of{\nu_\Gamma}{V^{[\Gamma]}\to P^{[\Gamma]}}$
and
$\Of{\varsigma^\tau_{\Upsilon\parallel\Gamma}}{P_\tau^{\Yoneda{\Upsilon\parallel\Gamma}}
\times S^{\{\Upsilon\}}\times P^{[\Gamma]}\to P_\tau}$.

@@

Next we have the interpretation of metavariable applications
\[%
  \SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
    \MApp{\MV{m}}{\vec{u}}{\vec{M}} : \tau}_P%
  \qquad(\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}})
\]
which proceeds by projecting the metavariable's interpretation from the
environment and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
          \arrow[r, "\IMode{\varsigma_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \& \IMode{P_s}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{align*}
  \ADefine{\phi}{
  \begin{tikzcd}[ampersand replacement = \&, sep=huge]
    {S^{\{\Upsilon\}}} \arrow[r, "\Tuple{\pi_u}_{u\in\vec{u}}"]
    \& {S^{\{\vec{\sigma}\}}}
  \end{tikzcd}
  }\\
  \ADefine{\psi}{
   \begin{tikzcd}[ampersand replacement = \&, sep=28ex]
     {\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}
        \arrow[r, "\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in \vec{M}\otimes\vec{\tau}}"]
     \& {P^{[\vec{\tau}]}}
   \end{tikzcd}
  }
\end{align*}
